Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-03-07 scnn.tex
further edits

As a hard constraint resulting from the cosmological applications, we are bound to use the HealPix sampling~\cite{gorski2005healpix} and we create a weighted undirected graph where each pixel is a node (vertex) that is connected to his $8$ or $7$ closest neighboors\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well defined.}. Given the set of nearest neighbors, we define the weight matrix $W$ using the following scheme
\begin{equation}
W[i,j]=\begin{cases}
e^{-\frac{\|x_i-x_j\|_2^2}{\sigma^2}} & \text{if pixels $i$ and $j$ are connected, and}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}
Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$ on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected pixels $i$ and $j$. The degree of a node (or a pixel) is defined as $d_i = \sum_j W[i,j]$. The degree matrix $D$ is the diagonal matrix where $D_ii=d_i$.

>>>>

From the ubiquitous HealPix sampling~\citep{gorski2005healpix}, we create a weighted undirected graph where each pixel is a node (vertex) that is connected to his $8$ or $7$ closest neighbors.\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well defined.} Given the set of nearest neighbors, we define the weight matrix $W$ using the following scheme
\begin{equation}
W[i,j]=\begin{cases}
e^{-\frac{\|x_i-x_j\|_2^2}{\sigma^2}} & \text{if pixels $i$ and $j$ are connected, and}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}
Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$ on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected pixels $i$ and $j$. The degree of a node (or a pixel) is defined as $d_i = \sum_j W[i,j]$. The degree matrix $D$ is the diagonal matrix where $D_{ii}=d_i$.
